### 2011-12-10 docs/FAQ/faq.tex
add abort_maestro

   On some machines it does---Fortran 95 specifies that any local
   allocated arrays are automatically deallocated when a subroutine
   ends.  Fortran 90 does not do this.  Most MAESTRO routines rely 
   on this Fortran 95 feature.

   On IBM machines, for instance, using {\tt xlf90} instead of {\tt
     xlf95} for MAESTRO will produce memory leaks.

@@

\item {\em  MAESTRO crashes because the multigrid algorithm fails to
    converge---how do I get around this?}

@@

@@

\item {\em How can I force the code to output a plotfile at the next
   step?}

@@

@@

 No.  This is a design decision.  There is no support for axisymmetric
 coordinates in MAESTRO.  Spherical problems must be run in 3-d.

>>>>

   On some machines it does---Fortran 95 specifies that any local
   allocated arrays are automatically deallocated when a subroutine
   ends.  Fortran 90 does not do this.  Most \maestro\ routines rely 
   on this Fortran 95 feature.

   On IBM machines, for instance, using {\tt xlf90} instead of {\tt
     xlf95} for \maestro\ will produce memory leaks.

@@

\item {\em  \maestro\ crashes because the multigrid algorithm fails to
    converge---how do I get around this?}

@@

\item{\em How can I force \maestro\ to abort?}

  In the output directory, do `{\tt touch .abort\_maestro}'.  This 
  will cause the code to write out a final checkpoint file, free up
  any allocated memory, and gracefully exit.  Be sure to remove the 
  {\tt .abort\_maestro} file before restarting the code in the 
  same directory.

@@

\item {\em How can I force the code to output a plotfile / checkpoint
  file at the next step?}

@@

   Similarly, creating the file {\tt .dump\_checkpoint} will force the
   output of a checkpoint file.

@@

 No.  This is a design decision.  There is no support for axisymmetric
 coordinates in \maestro.  Spherical problems must be run in 3-d.
